---
title: Twilight Label
format: html
editor: visual
---

This script walk you through the labeling of twilight and creation of the light map.

::: callout-tip
*Delete this block when you have read!*

**If you don't have light data, delete this file!**

-   The script is meant to be adapted according to your needs, so feel free to delete or modify: you can still check [the original version online]().
-   At the same time, keep this file general to all your tags.
-   It is assume that you have followed the GeoPressureManual entirely. Make sure you have done that!
-   In particular, the instruction on how to understand the output of this script and what do are provided in [the labeling instruction of the GeoPressureManual]().
-   The script is not meant to be run with "Run all". Use the "play" button of each chunk to run the script line-by-line.
-   Nothing is saved at the end of the script and it is meant to be like that. Only label file and config.yml should be edited. Use `geopressure.R` for the final run.
:::

```{r, setup}
# Choose the id 
id <- "91D"

# Set the directory to the project root
# Set the directory to the project root
knitr::opts_knit$set(root.dir = "C:/Users/pa5772ma/OneDrive - Lund University/Lund PhD/R tools/GeoPressureTemplate-3/Luscinialuscinia")
library(GeoPressureR)
library(ggplot2)
library(glue)
```

## Create tag

Start from an existing `tag`

```{r}
load(glue("./data/interim/{id}.RData"))
```

or generate from a new ones

```{r, eval=F}
tag <- tag_create(config::get("id", id),
  crop_start = config::get("crop_start", id),
  crop_end = config::get("crop_end", id)
) |>
  tag_label() |>
  tag_set_map(
    extent = config::get("extent", id),
    scale = config::get("scale", id),
    known = config::get("known", id)
  )

```

## Create Twilight

Generate the twilight automatically. Check that `twl_offset` allows for night/day being centered on the figure, otherwise edit accordingly

```{r}
tag <- twilight_create(
  tag,
  twl_thr = NULL, 
  twl_offset = -2
    #config::get("twl_offset", id)
)

plot(tag, type = "twilight")
```

## Annotate twilight

```{r}
twilight_label_write(tag)
)
```

Read and check the twilight annotation

```{r}
tag <- twilight_label_read(tag)
plot(tag, type = "twilight")
```

## Compute likelihood map

```{r}
tag <- geolight_map(tag, twl_calib_adjust =2)
```

`twl_calib_adjust` and `twl_llp` can generally be left to default, but add to `config.yml` if needed.

## Check

### Check calibration

```{r}
barW <- median(diff(tag$param$geolight_map$twl_calib$x)) / 2
plot(tag$param$geolight_map$twl_calib, xlim = c(85, 100))
rect(xleft = tag$param$geolight_map$twl_calib$x - barW, ybottom = 0, xright = tag$param$geolight_map$twl_calib$x + barW, ytop = tag$param$geolight_map$twl_calib$y, col = gray(0.5))
```

### Check light map

```{r}
plot(tag, type = "map_light")
plot(tag, type = "map")
```

### Check with pressure and trajectory

```{r, eval=F}
geopressureviz(tag)
```
